Abstractions for Type-Level Programming

### 2022-05-11 symposium.tex
Explain the Singleton bound in more details

The |apply| method is the entry point of our library.
It takes a regular expression and returns an instance of |Regex|.
Instead of directly accepting a |String| argument, that method takes a type parameter, |R|, which will be inferred by the compiler, and allows us to get our hands on a type-level instance of the regular expression's string (the |Singleton| bound is necessary to guide Scala's type inference).
% TODO: could you explain in more detail why "the Singleton bound is necessary to guide Scala’s type inference"?
We use that type-level string to instantiate the |Compile| type, which is our type-level analysis component.

@@

\noindent
Unfortunately, this naive solution does not handle regular expressions with nested capturing groups.
For example, in |"(A(B)?)"|, that solution incorrectly labels the first group as optional.
To overcome this problem, we update our solution to keep track of the number of opening and closing parentheses (|Lvl|), which allows us to differentiate closing parentheses of inner and outer groups%
\footnote{
For simplicity, our presentation treats all non-escaped parentheses as capturing group delimiters.
Our implementation also takes \lstinline!\\Q...\\E! quotations into account and ignores parentheses that appear in character classes.
}:

>>>>

The |apply| method is the entry point of our library.
It takes a regular expression and returns an instance of |Regex|.
Instead of directly accepting a |String| argument, that method takes a type parameter, |R|, which will be inferred by the compiler, and allows us to get our hands on a type-level instance of the regular expression's string\footnote{
\begin{diff}
The \texttt{Singleton} bound is a marker that instructs type inference to preserve unions and literal singleton types.
By default, the compiler widens those types, notably in method applications.
For instance, given \texttt{1} \texttt{::} \texttt{Nil}, Scala's default type inference yield \texttt{List[Int]} instead of the more precise \texttt{List[1]}.
To alter this behavior, one could mark \texttt{::}'s type argument with the \texttt{Singleton} bound.
\end{diff}
}.
We use that type-level string to instantiate the |Compile| type, which is our type-level analysis component.

@@

\noindent
Unfortunately, this naive solution does not handle regular expressions with nested capturing groups.
For example, in |"(A(B)?)"|, that solution incorrectly labels the first group as optional.
To overcome this problem, we update our solution to keep track of the number of opening and closing parentheses (|Lvl|), which allows us to differentiate closing parentheses of inner and outer groups%
\footnote{
For simplicity, our presentation treats all non-escaped parentheses as capturing group delimiters.
Our implementation also takes \texttt{\textbackslash{}Q...\textbackslash{}E} quotations into account and ignores parentheses that appear in character classes.
}:

### 2022-05-11 thesis.tex
Explain the Singleton bound in more details

\noindent
The |Singleton| type bound is a marker that instructs type inference to preserve union types and literal singleton types (by default, the compiler widens those types).
The "|?|" type is Scala~3's new syntax for wildcard types~\citep[Wildcard Arguments in Types]{odersky2013scala}.

>>>>

\noindent
The |Singleton| type bound is a marker that instructs type inference to preserve unions and literal singleton types (by default, the compiler widens those types).
The "|?|" type is Scala~3's new syntax for wildcard types~\citep[Wildcard Arguments in Types]{odersky2013scala}.
